Mitigating DDoS attacks in Named Data Networking

### 2012-11-29 paper.tex
Correcting abstract
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@832 df1a90cd-247b-4364-bdaf-287a704eb499

\documentclass[conference]{IEEEtran}
\title{Mitigating (D)DoS in Named-Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

@@

\begin{abstract}
%
abstract
%
\end{abstract}

\noindent {\bf Keywords:} Future Internet Architectures;
Content-Centric Networks; Information-Centric Networks, Named-data
Networking; Security; Denial-of-Service; Distributed
Denial-of-Service.

\section{Introduction \label{intro}}
Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.

Our contributions.

Paper organization.

\section{ CCN Overview\label{ccn-intro}}

\section { DDoS Attacks in CCN \label{ccn-ddos}}
Brief overview of possible attacks in CCN, and scope of what we will tackle in this paper (Interest flooding).

\section { Interest Flooding in CCN }

>>>>

\documentclass[10pt, conference, compsocconf]{IEEEtran}

\title{Mitigating DDoS attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

@@

\begin{abstract}

Distributed Denial of Service attack is an ongoing problem in today's Internet. 
A newly proposed future Internet architecture, Named Data Networking (NDN), lets end users request desired data by sending Interest packets, and the network forwards data packets to end users upon request only. 
Thus, NDN can effectively defeat the existing DDoS attacks, however it can be subject to new types of DoS attacks, namely Interest packet flooding.  
In this paper we investigate effective solutions to mitigate Interest flooding attacks. 
We use simulations to evaluate the design and our results show that our proposed solution can respond to Interest flooding attacks quickly, and that the inherent flow-balance property of NDN (i.e., one Interest packet retrieves at most one Data packet) can be used as a basis for effective DDoS mitigation algorithms.

\end{abstract}

\begin{IEEEkeywords}
Information-Centric Networks, Named-data Networking, Denial-of-Service
\end{IEEEkeywords}

\input{intro.tex}
\input{ndn-overview.tex}
\input{ddos-ndn.tex}
\section { Interest Flooding in CCN }
